Screening harmonies

### 2020-07-16 choosing_harmonies_Normal4.Rmd
cleaning and arranging files

@@

<!-- # Bibliography -->

<!-- ```{r write-bib, eval = FALSE} -->
<!-- write_bib(c("dplyr", "tidyr", "tsibble", "magrittr", "rlang", "gravitas", "knitr", "rmarkdown"), file = "rpkgs.bib") -->
<!-- ``` -->

# Does normalisation work?

```{r}
library(ggplot2)
library(gravitas)
sm <- smart_meter10 %>% dplyr::filter(customer_id %in% c("10017936"))

@@

.data = sm
response  = "general_supply_kwh"
harmony_tbl =  harmonies
smart_harmony <- .data %>% gravitas::rank_harmony(harmony_tbl = harmonies,
response = "general_supply_kwh", dist_ordered = FALSE)

smart_harmony %>% ggplot(aes(x = x_levels, y =  r)) + geom_point()
```

>>>>

# Does normalisation work?
(Show with by comparing with maximum and 
showing for similar levels)
# Does it match with the threshold?
# Should they tally with each other?

@@

```{r smart_harmony}
library(ggplot2)
library(gravitas)
sm <- smart_meter10 %>% dplyr::filter(customer_id %in% c("10017936"))

@@

harmony_tbl =  harmonies

smart_harmony <- sm %>% 
  rank_harmony(harmony_tbl = harmonies,
               response = "general_supply_kwh", 
               dist_ordered = FALSE)

smart_harmony %>% kable()

smart_harmony %>% ggplot(aes(x = x_levels, y =  r)) + geom_point()

smart_harmony %>% ggplot(aes(x = facet_levels, y =  r)) + geom_point()
```
